Presentation report

### 2024-06-25 Docs/Presentation.Rmd
meeting notes on the manuscript

```{r nhanes_exp, fig.width=8, fig.height=5}
df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
df_nhanes %>% 
  select(SEQN, Z, sind) %>% 
  filter(SEQN %in% sample(unique(df_nhanes$SEQN), size = 100)) %>%
  filter(Z == 1) %>%
  ggplot()+
  geom_point(aes(x=sind, y=SEQN), size = 0.2)+
  labs(x = "")+
  labs(x = "Time", y="Subject")+
  scale_x_continuous(breaks = seq(0, 1440, by = 360),
                     labels = c("0am", "6am", "12pm", "6pm", "12am"))+
  theme(axis.text.y = element_blank())

@@

```{r load_nhanes}
# df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput_fGFPCA.RData"))
load(here("Data/ApplOutput_GLMMadaptive.RData"))

>>>>

```{r load_nhanes}
# binary
df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))

# continuous
df_nhanes_cont <- read_rds(here("Data/NHANES_AC_processed.rds"))
df_exp <- df_nhanes_cont %>%
  filter(SEQN == 21910 | SEQN == 29599) %>%
  filter(WEEKDAY==5) %>% 
  group_by(Gender) %>%
  sample_n(1) %>%
  select(SEQN, Gender, starts_with("MIN")) %>%
  pivot_longer(starts_with("MIN")) %>%
  mutate(minute = as.numeric(gsub("MIN", "", name))) %>%
  mutate(value_bi = value > 100)

@@

```{r cont_func_exp, fig.height=4, fig.width=6}
df_exp %>%
  ggplot(aes(x=minute, y=value, col=Gender))+
  geom_point(size = 0.5, alpha = 0.5)+
  geom_smooth(method = "loess", formula = y ~ x, show.legend = F)+
  # scale_y_continuous(transform = "log")+
  scale_color_manual(values = c("#FC8D62", "#8DA0CB"))+
  scale_x_continuous(breaks = seq(0, 1440, by = 360),
                     labels = c("0am", "6am", "12pm", "6pm", "12am"))+
  labs(y = "Activity count", x="")
```

```{r gen_func_exp, fig.height=4, fig.width=6}
df_exp %>%
  filter(value_bi) %>% 
  ggplot(aes(x=minute, y=Gender, col=Gender))+
  geom_point(size = 0.5, alpha = 0.5, show.legend = F)+
  # scale_y_continuous(transform = "log")+
  scale_color_manual(values = c("#FC8D62", "#8DA0CB"))+
  scale_x_continuous(breaks = seq(0, 1440, by = 360),
                     labels = c("0am", "6am", "12pm", "6pm", "12am"))+
  labs(y = "Activity indicator", x="")
```

```{r nhanes_exp, fig.width=8, fig.height=5}
df_nhanes %>% 
  select(SEQN, Z, sind) %>% 
  filter(SEQN %in% sample(unique(df_nhanes$SEQN), size = 100)) %>%
  filter(Z == 1) %>%
  ggplot()+
  geom_point(aes(x=sind, y=SEQN), size = 0.2)+
  labs(x = "")+
  labs(x = "Time", y="Subject")+
  scale_x_continuous(breaks = seq(0, 1440, by = 360),
                     labels = c("0am", "6am", "12pm", "6pm", "12am"))+
  theme(axis.text.y = element_blank())

```{r load_nhanes_result}
# df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput_fGFPCA.RData"))
load(here("Data/ApplOutput_GLMMadaptive.RData"))
